---
title: "Functional programming Lab 1"
author: "Meghan Siritzky, Lea Frank, Wanjia Guo, and Sarah Dimakis"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    theme: yeti
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
              	   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

# 1. From the model results 

Extract the qr tolerance (tol).

```{r}
qr(m)$tol
```

Extract the qr tolerance (tol).

```{r}
model <- attributes(m$model)
terms <- attributes(model$terms)
terms$term.labels
```

# 2. From the list results

```{r}
str(l)
```

Use at least two different methods to extract m.

```{r}
l$a$m

l[[1]][[1]]
```

Extract the third column of m. Maintain the dimensions (matrix structure).

```{r}
l$a$m[,3, drop = FALSE]
```

Extract the score for student 7.

```{r}
str(l)
l$b$score[7]
```

# 3. Use the “airquality” dataset, which is part of base R. Split it by `Month`

```{r}
by_month <- split(airquality, airquality$Month)

str(by_month)
```

# 4. Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

```{r}
mean_ozone <- rep(NA, length(by_month))

for (i in seq_along(by_month)) {
  mean_ozone[i] <- mean(by_month[[i]]$Ozone, na.rm = TRUE)
}

mean_ozone
```

# 5. Replicate this calculation with lapply, sapply, and vapply

```{r}
mean_ozone1 <- lapply(mean_ozone, mean, na.rm = TRUE)
mean_ozone1

mean_ozone2 <- sapply(mean_ozone, mean, na.rm = TRUE)
mean_ozone2

mean_ozone3 <- vapply(mean_ozone, mean, FUN.VALUE = double(1))
mean_ozone3
```

# 6. Produce separate plots showing the relation between Ozone and Solar.R for each month

```{r, warning = FALSE, message = FALSE}
library(ggplot2)

(plots <- lapply(by_month, function(x) {
  ggplot(x, aes(Ozone, Solar.R)) +
  geom_point(color = "gray40") +
  geom_smooth(method = "lm", color = "red") +
  theme_minimal()}))

```

# 7. Use a for loop to save the plots to a folder on your computer

```{r}
filenames <- here::here("lab_1", "images", 
                        paste0("month", names(by_month), ".png"))
filenames

```

```{r, eval = FALSE}
for(i in seq_along(plots)) {
    ggsave(filenames[i], 
           plots[[i]], 
           device = "png",
           width = 7, 
           height = 5)
}
```


