---
title: "Functional programming Midterm"
author: "Meg Siritzky, Lea Frank, Wanjia Guo, and Sarah Dimakis"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    theme: flatly
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
```

# Part A

## 1. Briefly name and describe the three fundamental components of a function.

+ `formals()` - This refers to the arguments that can be supplied to a function (e.g. `data = ` or `na.rm = TRUE`)
\n
+ `body()` - This is the code that makes up the function. The `body()` code runs with the supplied arguments and returns some output.
\n
+ `environment()` - This refers to where the function is saved. For example, it could be saved in your Global Environment, or it may be saved in a package. 

## 2. Describe three different ways functions can be stored/applied and an example of when you might want to use each version.

+ If you have to repeat the same chunk of code multiple times, it could be easier to write that code into a function and save it as an object in your Global Environment. For example, if you are reading in multiple data files that all require the same data cleaning, you could write the data cleaning steps into a single function and iterate that function over the data files.
\n
+ If you are just applying those data cleaning steps in one part of your code, you could instead write an anonymous function that gets iterated within `purrr::map*` or base `*apply` functions. In these instances, the function is not saved as an object within the Global Environment. 
\n
+ If you have a list of functions that you want to apply over multiple iterations, you can save them into a list. For example, if you want to generate multiple plots using custom functions, you can save the custom plotting functions into a list. You can then loop through the functions to generate the plots. This can be even more powerful when you need to generate the same set of plots using multiple data files. 

# Part B

## 1

```{r}
mymean <- function(x){
  if(is.numeric(x)){
    if(any(is.na(x)) == FALSE){
      sum(x)/length(x)
    }
    else{
      warning(sum(is.na(x)), " cases of missing data were removed")
      z <- na.omit(x)
      sum(z)/length(z)
    }
  }
  else{
    warning("This function only accepts numeric values. Returning NA.")
    return(NA)
  }
}

```

## 2

```{r}
#Vector with 3 NAs has warning
test1 <- c(1, 3, 5, 6, 7, 3, 4, 6, NA, NA, NA)
mymean(test1)
mean(test1, na.rm = TRUE)

#Vector without NAs does not have warning
test2 <- c(1, 3, 5, 6, 7, 3, 4, 6)
mymean(test2)
mean(test2, na.rm = TRUE)

#Vector with a non-numeric item has warning
test3 <- c("1", 3, 5, 6, 7, 3, 4, 6)
mymean(test3)
mean(test3, na.rm = TRUE)


```

## 3

```{r}

```


## 4
```{r}
num_cols <- function(df){
  num <- map_lgl(df, is.numeric)
  if(sum(num) == 0){
      warning("There are no numeric variables in your dataset.")
    return()}
  else{
    num_l <- df[num]
    num_l}
}
```

```{r}
# Testing

library(palmerpenguins)
str(penguins)
str(num_cols(penguins))


df1 <- tibble(x = c(1,2,3), y = c("a", "b", "c"))
df2 <- tibble(w = c(1,2,3), x = c("a", "b", "c"), y = c(4,5,6), z = c("d", "e", "f"))
df3 <- tibble(x = c("b","c", "z"), y = c("a", "b", "c"))
df4 <- tibble(x = c(1.5,2.1,3), y = c(6L, 4L, 3L))
df5 <- tibble(x = c(1.5,2, NA), y = c(6L, 4L, 3L))

#a case with one numeric
df1 
num_cols(df1)

# a case with two numeric
df2
num_cols(df2)

# a case with no numeric
df3
num_cols(df3)

# a case with only numeric
df4
num_cols(df4)

#a case with missing data
df5
num_cols(df5)

```

## 5

```{r}

summary_cols <- function(df){
  if(length(num_cols(df)) != 0){
    mean <- map_dbl(num_cols(df), ~mean(.x, na.rm = TRUE))
    sd <- map_dbl(num_cols(df), ~sd(.x, na.rm = TRUE))
    if(length(num_cols(df)) == length(df)){
      tibble(column = names(df), mean = mean, sd = sd)
    }
    else{
      num <- map_lgl(df, is.numeric)
      var <- df[!num]
      warning(paste("The variable(s)", paste(names(var), collapse=", "), "have been ommitted because they are not numeric."))
      tibble(column = names(num_cols(df)), mean = mean, sd = sd)
    }
  }
  else{
    return()
  }
}


# warning message when one is not numeric
summary_cols(df1)

#warning message when two are not numeric 
summary_cols(df2)

# warns you when there are no numeric variables 
summary_cols(df3)

# no message when all numeric
summary_cols(df4)

# automatically removes NAs when calculating mean, sd
summary_cols(df5)

#big dataset
summary_cols(penguins)
```
